Untitled

### 2024-08-27 code/manuscript_analysis.Rmd
remove anticipation from model

qnats1 <- seq(0, 5/6, by = 1/6)
qnats2 <- seq(1/6, 1, by = 1/6)

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0, 1, Tx)), 
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    tes <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:6){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0 , 1, Tx)) , 
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

zp.pats <- tes[-1,] %>% 
  cbind(Quantile = 1:6) %>% 
  ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Estimate")

@@

model <- did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 )%>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.far <- rbind(TEs.strat.far, data.frame(model$coeftable)[1,])
}

model <- did2s(
      data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.close <- rbind(TEs.strat.close, data.frame(model$coeftable)[1,])
}

@@

df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% 
  group_by(Tx) %>% 
  summarise(mean(Sites))

>>>>

qnats1 <- seq(0, 4/5, by = 1/5)
qnats2 <- seq(1/5, 1, by = 1/5)

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0, 1, Tx))%>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))),  
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    tes <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:5){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0 , 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

zp.pats <- tes[-1,] %>% 
  cbind(Quantile = 1:5) %>% 
  ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Estimate")

@@

quantile(df.spill3$Dist, 0.15, na.rm = TRUE)

model <- did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) #%>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.far <- rbind(TEs.strat.far, data.frame(model$coeftable)[1,])
}

model <- did2s(
      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) #%>%  mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.close <- rbind(TEs.strat.close, data.frame(model$coeftable)[1,])
}

@@
